Abstract Plots

### 2021-07-27 Abstract.Rmd
Evaluated performance characteristics with varying mutational load.

>>>>

# Mutational load performance characteristics

## Mutational load predictions

```{r}
step = seq(50, 1000, by = 50)
MMR.probabilities <- vector(mode = "list", length = length(step))
MMR.truth <- vector(mode = "list", length = length(step))

for (x in 1:length(step)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2)
  ffpe.truth <- rep("FFPE", step[x]/2)
  sample.sig6 <- create_signature_sample_vector(cosmic.sig6, step[x]/2)
  sig6.truth <- rep("MMR", step[x]/2)
  test <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"),
                                list(cosmic.sig6, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "MMR",1,0))

  MMR.probabilities[[x]] <- classification$MMR
  MMR.truth[[x]] <- classification$trueBinary
}
```

```{r}
step = seq(50, 1000, by = 50)
tob.probabilities <- vector(mode = "list", length = length(step))
tob.truth <- vector(mode = "list", length = length(step))

for (x in 1:length(step)){
  sample.ffpe <- create_signature_sample_vector(ffpe.sig, step[x]/2)
  ffpe.truth <- rep("FFPE", step[x]/2)
  sample.sig4 <- create_signature_sample_vector(cosmic.sig4, step[x]/2)
  sig4.truth <- rep("tob", step[x]/2)
  test <- get_classification_df(list(sample.sig4, sample.ffpe), c("Tobacco","FFPE"),
                                list(cosmic.sig4, ffpe.sig))
  classification <- test %>%
    mutate(trueBinary = ifelse(truth == "Tobacco",1,0))

  tob.probabilities[[x]] <- classification$Tobacco
  tob.truth[[x]] <- classification$trueBinary
}
```

```{r}
load.MMR <- prediction(MMR.probabilities, MMR.truth)
load.tob <- prediction(tob.probabilities, tob.truth)
```

```{r}
AVG.sens.MMR <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  sens.MMR <- performance(load.MMR, measure = "sens")

load.sens.MMR.vec = c()
for (avg in 1:length(AVG.sens.MMR)){
  load.sens.MMR.vec[avg] = mean(AVG.sens.MMR[[avg]], na.rm = TRUE)
}
```

```{r}
AVG.sens.tob <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  sens.tob <- performance(load.tob, measure = "sens")

load.sens.tob.vec = c()
for (avg in 1:length(AVG.sens.tob)){
  load.sens.tob.vec[avg] = mean(AVG.sens.tob[[avg]], na.rm = TRUE)
}
```

```{r}
#plot(step, load.sens.MMR.vec, ylim = c(0,1))
sensitivity = append(load.sens.MMR.vec, load.sens.tob.vec)
signature.sens = append(rep("MMR", length(load.sens.MMR.vec)),
                        rep("Tobacco", length(load.sens.tob.vec)))
dilution = append(step, step)
sens.df <- data.frame(dilution, sensitivity, signature.sens)

ggplot(data = sens.df, mapping = aes(x = dilution, 
                                     y = sensitivity, 
                                     color = signature.sens)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Specificity value") +
  coord_cartesian(ylim = c(0,1))
```

```{r}
AVG.spec.MMR <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  spec.MMR <- performance(load.MMR, measure = "spec")

load.spec.MMR.vec = c()
for (avg in 1:length(AVG.spec.MMR)){
  load.spec.MMR.vec[avg] = mean(AVG.spec.MMR[[avg]], na.rm = TRUE)
}
```

```{r}
AVG.spec.tob <- vector(mode = "list", length = length(step))

for (iteration in 1:100){
  spec.tob <- performance(load.tob, measure = "spec")

load.spec.tob.vec = c()
for (avg in 1:length(AVG.spec.tob)){
  load.spec.tob.vec[avg] = mean(AVG.spec.tob[[avg]], na.rm = TRUE)
}
```

```{r}
#plot(step, load.spec.MMR.vec, ylim = c(0,1))

specificity = append(load.spec.MMR.vec, load.spec.tob.vec)
signature.spec = append(rep("MMR", length(load.spec.MMR.vec)),
                        rep("Tobacco", length(load.spec.tob.vec)))
dilution = append(step, step)
spec.df <- data.frame(dilution, specificity, signature.spec)

ggplot(data = spec.df, mapping = aes(x = dilution, 
                                     y = specificity, 
                                     color = signature.spec)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Specificity as a function of mutational load",
       x = "Number of mutations in each sample",
       y = "Specificity value") +
  coord_cartesian(ylim = c(0,1))
```
